---
title: "Sea-Level Rise Management Network"
author: "Center for Environmental Policy and Behavior, UC Davis"
output: html_document
---

This a network of organizations working on projects to address sea-level rise. There are two types of nodes: projects and organizations. Organizations are connected to the projects in which they participate. You can examine a project's participants using the first dropdown menu by selecting by id. You can also look at which projects and organizations work in a particular county using the second dropdown menu. 

Try zooming in on part of the graph and clicking on a project or organization.

```{r setup, include=FALSE}
# Some options:
visColors = c(org = "dodgerblue", proj = "firebrick")
shadows = FALSE   # They maybe look cool but significantly slow performance

library(tidyverse)
library(stringr)
library(visNetwork)
library(igraph)
edges <- read_csv("data/EdgelistIn.csv")
nodes <- read_csv("data/Attributes.csv")

# at$Entity has "1" or "2" prepended based on type. Remove that and rename "id"
nodes = nodes %>%
  mutate(Entity = str_sub(Entity, 2)) %>%
  rename(id = Entity)

edges = edges %>%
  rename(from = Org, to = Proj)

# Temporary subset to make rendering faster
# projtmp = head(unique(edges$to))
# edges = filter(edges, to %in% projtmp)
# nodes = filter(nodes, id %in% unique(c(projtmp, edges$from)))

# Get counties in single column, comma-separated format for visOptions
# Pull out the county columns, look for "1" entries, and replace with colnames
counties = select(nodes, Alameda:`Online Only`) 
presence = which(counties == 1, arr.ind = TRUE)
counties[presence] = colnames(counties)[presence[, 2]]
# Collapse non-empty columns with comma separator
nodes$County = apply(counties, 1, function(x) paste(x[!is.na(x)], collapse = ", "))

# Make column names that visNetwork uses
nodes = nodes %>%
  mutate(label = id,
         title = id,
         color = visColors[BiType],
         shape = c("box", "diamond")[BiType]
  )

### Remove energy projects
# find energy projects by Type.Name
energyProj = unique(nodes$id[nodes$Type.Name == "Energy"])  
# Find orgs working on energy projects
energyOrgs = unique(edges$from[edges$to %in% energyProj])  
# Filter edges to exclude energy projects
edges = filter(edges, !to %in% energyProj)
# See which energy-orgs are no longer in the edgelist...
energyOnlyOrgs = unique(energyOrgs[!energyOrgs %in% edges$from])
# remove those and energy projects from nodes
nodes = filter(nodes, !id %in% c(energyOnlyOrgs, energyProj))

# Add degree to node DF to size icons
nodes = 
  as.data.frame(table(unlist(edges))) %>%
  rename(id = Var1, degree = Freq) %>%
  left_join(nodes, ., by = "id")
nodes$value = nodes$degree 
nodes$value[nodes$BiType == 1] = 1  # Doesn't do anything because "box" doesn't take a size.

# Prepend "Project" or "Organization" to names for select-by drop-down.
# Wasn't able to get this working (in visOptions). 
# Instead let user select only projects (not orgs), by "id"
# nodes$menuLabel = paste0(ifelse(nodes$BiType == 1, "Organization: ", "Project: "), nodes$id)

# Get layout coordinates and append to nodes DF to speed initial layout
# g = graph_from_data_frame(edges, FALSE, nodes)
# coords = layout_nicely(g)
# colnames(coords) = c("x", "y")
# nodes = cbind(nodes, coords)


```

```{r output, echo = FALSE, fig.height = 9, fig.width = 10}
# Render the network
visNetwork(nodes, edges) %>%
  visNodes(shadow = shadows) %>%
  visEdges(shadow = shadows
           , color = "gray"
           , selectionWidth = 3
           # , smooth = FALSE   # FALSE is faster but TRUE gives nicely curved edges. Doesn't apply for igraph layout
  ) %>%
  visOptions(
    # Enable select by county
    selectedBy = list(variable = "County", multiple = TRUE)
    # Enable select by ID and highlight associated orgs/projects
    , nodesIdSelection = list(enabled = TRUE 
                              , values = nodes$id[nodes$BiType == 2] # values = "menuLabel" doesn't work
                              )
    , highlightNearest = list(enabled = TRUE, degree = 1, hover = TRUE)
  ) %>%
  visLegend(addNodes = list(
    list(label = "Organization", shape = "box", color = visColors[[1]]),
    list(label = "Project", shape = "diamond", color = visColors[[2]])),
    useGroups = FALSE,
    position = "right",
    width = .1) %>%
  # Static igraph layout:
  # visIgraphLayout(smooth = FALSE, physics = FALSE, type = "full", randomSeed = 95616)
  # Dynamic igraph layout. Doesn't equilibrate:
  # visIgraphLayout(smooth = TRUE, physics = TRUE, type = "full",
  #                 layout = "layout_nicely")
  # Physics simulation dynamic. Equilibrates layout in ~40s w/ vel = 30/15
  visPhysics(stabilization = FALSE
             # , maxVelocity = 30
             , minVelocity = 15
             , solver = "repulsion"
             # , repulsion = list(
             #   springLength = 250
             #   , springConstant = .1
             #   , centralGravity = .15
             #   # , nodeDistance = 75
             # )
             # , solver = "barnesHut"
             # , barnesHut = list(gravitationalConstant = -1e3
             #                    , centralGravity = .2
             #                    , springConstant = .1
             #                    , springLength = 200)
             ) %>%
  visEvents(type = "once", startStabilizing = "function() {
            this.moveTo({scale:.3})}") 
  # Nearly equil w defaults at 30"
  # visPhysics(stabilization = FALSE
  #            , solver = "forceAtlas2Based"
  #            , minVelocity = 5
  #            , maxVelocity = 30
  # )
```

